A Partitioning Algorithm for Maximum Common Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-14 paper/paper.tex
Highlighted a section which may need to be re-worded

In the constraint programming approach  \cite{DBLP:conf/cp/NdiayeS11}, a variable corresponds to
each vertex in $G$, and each variable initially has one value in its domain for
each vertex in $H$ to which it may be mapped, plus an additional value $\bot$
signifying that the vertex remains unmapped. A backtracking search is performed
in which values are assigned to variables, and propagation rules are used to
remove infeasible values from domains.  A matching algorithm propagates
a soft global allDifferent constraint which maximizes the number variables that are assigned to values different from $\bot$, while ensuring they are all different when they are not assigned to $\bot$.
Different constraint propagation techniques are compared in \cite{DBLP:conf/cp/NdiayeS11}. The combination ``MAC+Bound'' (resp. ``FC+Bound'') obtains the best results on labelled (resp. non labelled) graphs and outperforms the approach of \cite{McGreg82} and the CP model of \cite{DBLP:conf/mco/VismaraV08}. The combination ``MAC+Bound'' maintains arc consistency~\cite{sabi94} of edge constraints, whereas the conbination ``FC+Bound'' simply performs forward-checking on these constraints. In both combinations, the ``Bound'' filtering checks whether it is possible to assign distinct values to enough variables to surpass the best cost found so far (it is a weaker version of GAC(\emph{softAllDiff}) \cite{peti01} which computes the maximum number of variables that can be assigned distinct values).

>>>>

In the constraint programming approach  \cite{DBLP:conf/cp/NdiayeS11}, a variable corresponds to
each vertex in $G$, and each variable initially has one value in its domain for
each vertex in $H$ to which it may be mapped, plus an additional value $\bot$
signifying that the vertex remains unmapped. A backtracking search is performed
in which values are assigned to variables, and propagation rules are used to
remove infeasible values from domains.
\textit{A matching algorithm propagates
a soft global allDifferent constraint which maximizes the number variables that are assigned to values different from $\bot$, while ensuring they are all different when they are not assigned to $\bot$.
Different constraint propagation techniques are compared in \cite{DBLP:conf/cp/NdiayeS11}. The combination ``MAC+Bound'' (resp. ``FC+Bound'') obtains the best results on labelled (resp. non labelled) graphs and outperforms the approach of \cite{McGreg82} and the CP model of \cite{DBLP:conf/mco/VismaraV08}. The combination ``MAC+Bound'' maintains arc consistency~\cite{sabi94} of edge constraints, whereas the conbination ``FC+Bound'' simply performs forward-checking on these constraints. In both combinations, the ``Bound'' filtering checks whether it is possible to assign distinct values to enough variables to surpass the best cost found so far (it is a weaker version of GAC(\emph{softAllDiff}) \cite{peti01} which computes the maximum number of variables that can be assigned distinct values).}
